---
title: "MetCirc: Navigating mass spectral similarity in high-resolution 
    MS/MS metabolomics data"
author:
 - name: Thomas Naake and Emmanuel Gaquerel
   mail: thomas.naake@embl.de, thomasnaake@googlemail.com
   affiliation: 
        European Molecular Biology Laboratory, 69117 Heidelberg, Germany; 
        Institut de biologie mol\'{e}culaire du m\'{e}tabolisme des plantes,
        Universit\'{e} de Strasbourg, 67084 Strasbourg, France
package: MetCirc
      
output:  
    BiocStyle::html_document:
        toc_float: true
bibliography: MetCirc-citations.bib
vignette: >
    %\VignetteIndexEntry{Workflow for Metabolomics}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteKeywords{Mass Spectrometry, MS, MSMS, Metabolomics, Visualization}
    %\VignettePackage{MetCirc-vignette}
    %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

```{r env, include=FALSE, echo=FALSE, cache=FALSE}
library("knitr")
opts_chunk$set(stop_on_error = 1L)
suppressPackageStartupMessages(library("MetCirc"))
```

# Introduction

The `MetCirc` package comprises functionalities to display, 
(interactively) explore similarities and annotate features of MS/MS metabolomics 
data. It is especially designed to 
improve the interactive exploration of metabolomics data obtained from 
cross-species/cross-tissues comparative experiments. `MetCirc` relies
on the `Spectra` infrastructure to handle MS/MS spectra. Specifically,
`MetCirc` uses the Spectra` class from which similarities 
between features are calculated and which stores 
information on spectra in the columns of the slot `metadata`.

Notably, `MetCirc` 
provides functions to calculate the similarity between individual MS/MS 
spectra based on a normalised dot product (NDP, see @Li2015 for further 
details) calculation taking into account shared fragments or main neutral 
losses. 

Visualisation of molecular networks was pioneered by the Dorrestein lab 
[@Watrous2012] to efficiently organize MS/MS spectra in such a 
way that clusters of MS/MS spectra sharing multiple common fragments are rapidly 
inferred. 

In contrary to the analysis there, the `MetCirc` framework offers two 
ways for the computation of mass spectrum similarity: one way deploys common
(shared) fragments and the other shared neutral losses that are deduced from 
the spectra. Especially the latter 
approach allows to extract clusters of spectra corresponding to compound families 
facilitating the rapid dereplication of hitherto unknown metabolites. Small 
molecules, as produced by plants, return during fragmentation few fragments.  
Sometimes only a few fragments among them are shared and diagnostic across 
the compound family. Compared to the 
MS/MS similarity scoring based on shared fragments, the second similarity 
measure incorporates, in a non-supervised manner, neutral losses, which 
definitely helps obtaining biochemically-meaningful MS/MS groupings. 
Furthermore, any
other function to calculate similarities can be provided or a similarity 
matrix providing similarity (in the range from 0 to 1) for features that 
are present in the `Spectra` object. 

The interpretation drawn from network reconstruction highly depends 
from topological parameters applied during the network construction steps. 
`MetCirc` circumvents this confinement. Furthermore, it uses instead
smaller MS/MS datasets obtained from experiments involving 
*a priori* defined biological groups (organisms, tissues, etc.) to 
visualize within and between MS/MS feature similarities on a circular 
layout - inspired by the Circos framework [@Krzywinkski2009]. The 
visualisation is adjustable (MS/MS ordering and similarity thresholds) via the 
`shiny` interface and does not uniquely emphasize on large clusters 
of MS/MS features (a frequent caveat of network visualisation). Furthermore,
the implemented functionality for annotation may improve 
dereplication of known and unknown molecules. 

This vignette uses as a case study indiscriminant MS/MS (idMS/MS) data from 
@Li2015, unpublished idMS/MS data 
collected from different organs of tobacco flowers and data from the 
Global Natural Product Social Molecular Networking (GNPS) library
to navigate through the 
analysis pipeline. The pipeline includes the creation of `Spectra`
objects, the calculation of a similarity measure (NDP), 
assignment to a similarity matrix and visualisation of similarity based 
on interactive and non-interactive graphical tools using the 
`circlize` framework [@Gu2014]. 

`MetCirc` is currently under active development. If you 
discover any bugs, typos or develop ideas of improving 
`MetCirc` feel free to raise an issue via 
[GitHub](https://github.com/tnaake/MetCirc) or 
send a mail to the developers. 

```{r knitr, include=FALSE, cache=FALSE}
library("knitr")
```

# Prepare the environment

To install `MetCirc` enter the following to the `R` console
```{r eval=FALSE}
if (!requireNamespace("BiocManager", quietly=TRUE))
    install.packages("BiocManager")
BiocManager::install("MetCirc")
```

Before starting, load the `MetCirc` package. This will also
load the required packages `Spectra`, `circlize`, 
`amap`, `scales` and `shiny`: 

```{r eval=TRUE}
library("MetCirc")
library("MsCoreUtils")
```

The central infrastructure class of the `MetCirc` package is the 
`Spectra` object. The `Spectra` objects stores information 
on precursor m/z, retention time, m/z and intensity values of fragments 
and possible additional information, e.g. to which class the MS/MS feature 
belong to, the identity of the MS/MS feature, information on the adduct of the
precursor, additional information. Furthermore, the `Spectra` object 
can host information under which condition (in which tissue, etc.) the 
MS/MS feature was detected. 

We provide here three examplary workflows to create `Spectra` from 
data frames that are loaded into R: 
(1) by loading a data frame with a minimum requirement of a column "id" (comprising unique identifiers
for MS/MS features) and of the columns "mz" and "intensity" comprising the
fragment ions and their intensities, respectively, or 
(2) by loading a data frame resembling a .MSP file object.  

## Load example data sets from @Li2015, tissue idMS/MS data and GNPS data


sd02_deconvoluted comprises 360 idMS/MS 
deconvoluted spectra with fragment ions (m/z, chromatographic retention time, relative
intensity in %) and a column with unique identifiers for MS/MS features (here, 
the corresponding principal component group with the 
precursor ion). The data set is derived from the study of @Li2015. 

```{r eval=TRUE,echo=c(1:2)}
## load data from Li et al., 2015
data("sd02_deconvoluted", package = "MetCirc")

## load binnedMSP
data("sd01_outputXCMS", package = "MetCirc")
#data("binnedMSP", package = "MetCirc")

## load similarityMat
data("similarityMat", package = "MetCirc")
```

The second data set comes from the data-independent MS/MS 
collection of different floral organs from tobacco plants. Using our pipeline, 
this data set will be used to visualize shared metabolites between tissues as 
well as structural relationships among within- and between-organ MS/MS spectra.
MS/MS data are merged across floral organs in one unique data file 
`idMSMStissueproject.Rdata` as `tissue`. Information on the 
organ-localisation of each MS/MS spectrum is stored in  
`compartmentTissue`. 

```{r eval=TRUE}
## load idMSMStissueproject
data("idMSMStissueproject", package = "MetCirc")
```

The third data set comes from the GNPS data base (downloaded at February 11, 2017 from: \\
[http://prime.psc.riken.jp/Metabolomics\_Software/MS-DIAL/MSMS-GNPS-Curated-Neg.msp](http://prime.psc.riken.jp/Metabolomics\_Software/MS-DIAL/MSMS-GNPS-Curated-Neg.msp)). 
It contains 22 MS/MS features (a truncated file of the original one) and
is formatted in the .MSP file format, a typical format for 
MS/MS libraries. The MS/MS spectra are (normally) separated by blank lines
and give information on the metabolite (its name, precursor m/z value, 
retention time, class, adduct ion) and contain additional information. 

```{r eval=TRUE,echo=c(1:2)}
## load data from GNPS
data("convertMsp2Spectra", package = "MetCirc")
```

# Prepare data for mass spectral similarity calculations


## Preparing the sd02\_deconvoluted data set for analysis

Here, we convert the examplatory data from @Li2015 into a 
`Spectra` object that is later used as the input for mass spectral 
similarity calculations. 
Data in the form of the data frame sd02_deconvoluted require columns that 
store the m/z values of fragments, the intensity values 
for the respective fragments and a column containing an "id". The latter
column contains information about the precursor ion and 
should be a unique descriptor for the MS/MS features. For instance, this column
may be the derived from the output of the `xcms`/`CAMERA` 
processing creating unique identifiers for each metabolite decoded in the column
"pcgroup". A pcgroup is defined as a peak correlation group obtained by this
workflow. It corresponds to a MS or MS/MS spectrum deconvoluted by `CAMERA`
and contains information about the precursor identity and its isotope cluster. 
The column "id" may additionally contain information 
about the precursor retention time. 

Create `Spectra` object from the data of @Li2015:

```{r eval=TRUE}
## get all MS/MS spectra
id_uniq <- unique(sd02_deconvoluted[, "id"])

## obtain precursor m/z from id_uniq
prec_mz <- lapply(strsplit(as.character(id_uniq), split = " _ "), "[", 2) |>
    unlist() |>
    as.numeric()

## obtain m/z from fragments per precursor m/z
mz_l <- lapply(id_uniq, 
    function(id_i) sd02_deconvoluted[sd02_deconvoluted[, "id"] == id_i, "mz"])

## obtain corresponding intensity values 
int_l <- lapply(id_uniq, 
    function(id_i) sd02_deconvoluted[sd02_deconvoluted[, "id"] == id_i, "intensity"]) 

## obtain retention time by averaging all retention time values
rt <- lapply(id_uniq, function(x) sd02_deconvoluted[sd02_deconvoluted[, "id"] == x, "rt"]) |>
    lapply(function(i) mean(i)) |>
    unlist()

## create list of Spectra objects, concatenate, and add metadata
sps_l <- lapply(seq_len(length(mz_l)), function(i) {
    spd <- S4Vectors::DataFrame(
        name = as.character(i),
        rtime = rt[i], 
        msLevel = 2L,
        precursorMz = prec_mz[i])
    spd$mz <- list(mz_l[[i]])
    spd$intensity <- list(int_l[[i]])
    Spectra::Spectra(spd)})
sps_li <- Reduce(c, sps_l)
sps_li@metadata <- data.frame(show = rep(TRUE, length(sps_l)))
```

Furthermore, further columns in the `data.frame` passed to 
`metadata` can be specified to host additional information, e.g.
metabolite name (column "names") and classes (column "classes"), adduct ion 
names (column "adduct"), further information (column "information"). 

## Preparing the floral organ data set for analysis

We would like to restrict the proof-of-function analysis to four tissues 
(sepal, SPL; limb, LIM; anther, ANT; 
style, STY). We will truncate `tissue` in order that it contains only
these instances belonging to these types of tissue. In a next step, we will 
create a `Spectra`-object, `spl` with information concerning
if the MS/MS features are found in the tissues SPL, LIM, ANT and STY. 

```{r eval=TRUE}
## get all MS/MS spectra
tissue <- tissue[tissue[, "id"] %in% compartmentTissue[, "mz_rt_pcgroup"], ]
id_uniq <- unique(tissue[, "id"])

## obtain precursor m/z from id_uniq
prec_mz <- lapply(strsplit(as.character(id_uniq), split = "_"), "[", 1) |>
    unlist() |>
    as.numeric()

## obtain m/z from fragments per precursor m/z
mz_l <- lapply(id_uniq, function(id_i) tissue[tissue[, "id"] == id_i, "mz"]) 

## obtain corresponding intensity values
int_l <- lapply(id_uniq, function(id_i) tissue[tissue[, "id"] == id_i, "intensity"])

## order mz and intensity values
int_l <- lapply(seq_along(int_l), function(i) int_l[[i]][order(mz_l[[i]])])
mz_l <- lapply(seq_along(mz_l), function(i) sort(mz_l[[i]]))

## obtain retention time by averaging all retention time values
rt <- lapply(id_uniq, function(x) tissue[tissue[, "id"] == x, "rt"]) |>
    lapply(FUN = mean) |>
    unlist()

## create list of Spectra objects and concatenate
sps_l <- lapply(seq_len(length(mz_l)), function(i) {
    spd <- S4Vectors::DataFrame(
        name = as.character(i),
        rtime = rt[i], 
        msLevel = 2L,
        precursorMz = prec_mz[i])
    spd$mz <- list(mz_l[[i]])
    spd$intensity <- list(int_l[[i]])
    Spectra::Spectra(spd)})
sps_tissue <- Reduce(c, sps_l)

## add metadata
## use SPL, LIM, ANT, STY for further analysis
sps_tissue@metadata <- data.frame(
    compartmentTissue[, c("SPL", "LIM", "ANT", "STY")])
```

## Preparing the GNPS data set for analysis 

Alternatively as mentioned above, an `Spectra`-object can also created 
from .MSP objects, 
that are typical data formats for storing MS/MS libraries. 
Required properties of such a data frame are the name of the metabolite
(row entry "NAME:"), the m/z value of the precursor ion ("PRECURSORMZ" or 
"EXACTMASS:"), retention time ("RETENTIONTIME:"), information on the number of 
peaks ("Num Peaks:") and information on 
fragments and peak areas (for further information see `convertMsp2Spectra`
and retrieve `data("convertMsp2Spectra", package = "MetCirc")` for a typical
msp data frame). 

Create `Spectra`-object from the GNPS .MSP file:

```{r eval=TRUE}
sps_msp <- convertMsp2Spectra(msp2spectra)
```


# Binning and calculation of similarity matrix

## Workflow for `tissue` data set using fragment ions 

### Calculation of the similarity matrix

The similarity matrix can be obtained by by the `Spectra` package 
function `compareSpectra` which takes a `Spectra` object and a 
function for the similarity calculation as input. 

The `MetCirc` package uses functions from the `Spectra` 
package to calculate pair-wise similarities between MS/MS features. The 
user can select the function (via `FUN`) how to calculate the similarity.
The function `ndotproduct` from the `MsCoreUtils` package
calculates the similarity coefficient 
between two MS/MS features using the normalised dot product (NDP). 
For a considered MS/MS pair, peak intensities of shared m/z values for 
precursor/fragment ions are employed as weights
$W_{S1, i}$ and $W_{S1, i}$ within the following formula: 

\begin{equation*}
    NDP = \frac{\sum(W_{S1, i} \cdot W_{S2, i}) ^ 2}{ \sum(W_{S1, i} ^ 2) * \sum(W_{S2, i} ^ 2) },
\end{equation*}

with S1 and S2 the spectra 1 and 2, respectively, of the i$th$ of j common peaks
differing by the tolerance parameter specified in `compareSpectra`'s
argument `binSize`. 

Weights are calculated according to $W = [ peak~intensity] ^{m} \cdot [m/z]^n$,
with m = 0.5 and n = 2 as default values as suggested by MassBank.
For further information see @Li2015. 

Similarly, the function `neutralloss` takes into account neutral 
losses between precursor m/z values and all fragments. 

Alternatively, the user can specify a custom-defined function to calculate
similarities between MS/MS features or use an implemented function in 
`Spectra`. 
The function `compareSpectra` returns a symmetrical squared 
similarity matrix with pair-wsie similarity coefficients between MS/MS 
features. 

```{r eval=TRUE}
## similarity Matrix 
similarityMat <- Spectra::compareSpectra(sps_tissue[1:100,], 
    FUN = MsCoreUtils::ndotproduct, ppm = 10, m = 0.5, n = 2)
colnames(similarityMat) <- rownames(similarityMat) <- sps_tissue$name[1:100]
```

`compareSpectra` returns a square matrix; in a next step, we add
the names of the `Spectra` MS/MS features as column and row names. 
The entries of the returned matrix have to be similarites cores ranging between 
0 and 1 that are  the pair-wise similarities between the MS/MS features. 

### Clustering/visualisation

At this stage, we would like to visualize 
the pair-wise similarities of MS/MS features after clustering them.
Many functions are available to cluster features such as `hclust`
from `stats`, `Mclust` from `mclust` or 
`hcluster` from `amap`. We would like to use the latter 
to cluster similar features. To cluster features and visualize the result (see 
figure \ref{fig:cluster}) we enter:

```{r cluster,eval=TRUE,fig.show='hide'}
## load package amap
hClustMSP <- hcluster(similarityMat, method="spearman")

## visualize clusters
plot(hClustMSP, labels = FALSE, xlab="", sub="")
```

\begin{figure}[h!]
    \center
    \includegraphics[scale=0.6]{./figure/cluster-1}
    \caption{Cluster dendrogramm for similarity matrix based on fragment 
    ion NDP calculation} \label{fig:cluster}
\end{figure}

To promote readibility we will not show labels. These can be printed to the 
\R~console by `colnames(similarityMat)[hClustMSP\$order]`. 

### Extraction of highly-related features using clustering

Within the `R` session the similarity matrix can be truncated by using the 
above-mentioned functions to retrieve a similarity matrix that contains 
highly-related MS/MS features. For instance, this might be needed when 
we want to analyse modules of high similarity, representing e.g. a certain 
metabolite class. By way of example, we extract in the following all features
from module 1 when defining three modules in total and define a new 
similarity matrix of highly-related features. This kind of matrix can be 
used in later analysis steps, e.g. in the analysis with `shinyCircos`.

```{r truncateGroup1,eval=TRUE,echo=TRUE}
## define three clusters
cutTreeMSP <- cutree(hClustMSP, k = 3)

## extract feature identifiers that belong to module 1
module1 <- names(cutTreeMSP)[as.vector(cutTreeMSP) == "1"] 

## create a new similarity matrix that contains only highly related features
similarityMat_module1 <- similarityMat[module1, module1]
```

# Visualisation using the `shiny`/`circlize` framework

`MetCirc`'s main functionality is to visualize metabolomics
data, exploring it interactively and annotate unknown features based on 
similarity to other (known) features. One of the key features of the implemented
interactive framework is, that groups can be compared. A group 
specifies the affiliation of the sample: it can be 
any biological identifier relevant to the comparitive experiment conducted,
e.g. it can be a specific tissue, different
times, different species, etc. The visualisation tools implemented in 
`MetCirc` allow then to display similarity between 
precursor ions between and/or within groups. 

`shinyCircos` uses the function`createLinkDf` which 
selects these precursor ions that have a similarity score (e.g. a normalised dot 
product) within the range defined by `lower` and `higher` to a precursor ion. 
Internally, in`shinyCircos`,`createLinkDf` will be 
called to produce a data.frame with link information based on the given 
thresholds. 

```{r eval=TRUE}
linkDf <- createLinkDf(similarityMatrix = similarityMat, sps = sps_tissue,
    condition = c("SPL", "LIM", "ANT", "STY"), lower = 0.5, upper = 1)
```

As we have calculated similarity coefficients between precursors, we would
like to visualize these connections interactively and explore the data. 
The `MetCirc` package implements`shinyCircos` 
that allows for such kind of exploration. It is based on the `shiny`
and on the `circlize` [@Gu2014] framework. Inside of`shinyCircos` 
information of precursor ions are displayed by (single-) clicking over precursors. 
Precursors can also be permanently selected by double-clicking on them. The similarity
coefficients can be thresholded by changing the slider input. Also, on the 
sidebar panel, the type of link to be displayed can be selected: 
should only links between groups be displayed, should only links within groups 
be displayed or should all links be displayed? Ordering inside of groups 
can be changed by selecting the respective option in the sidebar panel. 
Momentarily, there are options to reorder features based on clustering, 
the m/z or the retention time of the precursor ion. In the "Appearance" tab,
the size of the plot can be changed, as well as the precision of the 
displayed values for the m/z and retention time values. Please note, 
that the precision will only be changed in the text output (not in the 
graphical output). Also, the user can decide if the legend is displayed or not.

On exiting the shiny application
via the exit button in the sidebar panel, selected precursors will
be returned which are allocated here to `selectedFeatures`. 
`selectedFeatures` is a vector of the precursor names. 

By way of example, we would like to analyse the tissue data set focusing on 
the tissues "SPL", "LIM", "ANT" and "STY".

To start the shiny app, run

```{r eval=FALSE}
selectedFeatures <- shinyCircos(similarityMat, sps = sps_tissue, 
    condition = c("LIM", "ANT", "STY"))
```

in the console. This will load information stored in the `Spectra` 
object `sps_tissue` to the `shinyCircos` interface. 
Information (metabolite names and
class, adduct ion name and further information) will be printed to the 
interface when (single-)clicking on MS/MS features. Since this 
`Spectra` object did not contain any information about metabolite 
names, class, adduct ion name and further information, initally all fields for 
these instances are set to "Unkwown". Note, that on the 
sidebar on the right side text fields will appear, that allow for changing 
the annotation of the selected feature. Click "update annotation" to save the 
changes to the `Spectra`-object. On exiting `shinyCircos` via
the exit button, selected precursors and the (updated) `Spectra`-object will
be returned to the console. In the example above, enter 
`selectedFeatures$sps` to retrieve the `Spectra` object 
with updated annotation. 

`MetCirc` allows also to create such figures outside of an
interactive context, which might be helpful to create figures and export them 
e.g. in .pdf or .jpeg format.`shinyCircos` does currently not 
support to export figures as they can be easily rebuilt outside of 
`shinyCircos`; building figures outside of the interactive context
also promotes reproducibility of such figures.  

To rebuild the figure in a non-interactive environment, run 

```{r circos,eval=TRUE,results='hide',message=FALSE,fig.show='hide'}
## order similarity matrix according to retention time
condition <- c("SPL", "LIM", "ANT", "STY")
simM <- orderSimilarityMatrix(similarityMatrix = similarityMat, 
    sps = sps_tissue, type = "retentionTime", group = FALSE)
groupname <- rownames(simM)
inds <- MetCirc:::spectraCondition(sps_tissue, 
    condition = condition)
inds_match <- lapply(inds, function(x) {inds_match <- match(groupname, x)
    inds_match <- inds_match[!is.na(inds_match)]; x[inds_match]})
inds_cond <- lapply(seq_along(inds_match), 
    function(x) {
        if (length(inds_match[[x]]) > 0) {
            paste(condition[x], inds_match[[x]], sep = "_")
        } else character()
})
inds_cond <- unique(unlist(inds_cond))

## create link matrix
linkDf <- createLinkDf(similarityMatrix = simM, sps = sps_tissue, 
    condition = c("SPL", "LIM", "ANT", "STY"), lower = 0.9, upper = 1)
## cut link matrix (here: only display links between groups)
linkDf_cut <- cutLinkDf(linkDf = linkDf, type = "inter")

## set circlize paramters
circos.par(gap.degree = 0, cell.padding = c(0, 0, 0, 0), 
    track.margin = c(0, 0))

## here set indSelected arbitrarily
indSelected <- 14
selectedFeatures <- inds_cond[indSelected]

## actual plotting
plotCircos(inds_cond, linkDf_cut, initialize = TRUE, featureNames = TRUE, 
    cexFeatureNames = 0.2, groupSector = TRUE, groupName = FALSE, 
    links = FALSE, highlight = TRUE)

highlight(groupname = inds_cond, ind = indSelected, linkDf = linkDf_cut)

## plot without highlighting
plotCircos(inds_cond, linkDf_cut, initialize = TRUE, featureNames = TRUE, 
    cexFeatureNames = 0.2, groupSector = TRUE, groupName = FALSE, links = TRUE, 
    highlight = FALSE)
```

\begin{figure}[h!]
    \center
    \includegraphics{./figure/circos-1}
    \caption{Examplary circos plot highlighting an arbitrary feature. Upon
        highlighting, all links will be plotted in grey (expect links to and 
        from highlighted features). The intensity
        of the background colour of features will be reduced as well. Features
        belonging to a group (species, individual, organ, different time) will 
        be indicated by the same background colour.}
\end{figure}

# Appendix {-}

## Session information {-}

All software and respective versions to build this vignette are listed here:

```{r session,eval=TRUE,echo=FALSE}
sessionInfo()
```


## Neutral losses {-}
\begin{longtable}{l | l } 
    \caption{The table gives examplatory fractionation of precursors 
    into neutral losses (given their m/z and the corresponding atoms):} 
    \label{tab:neutrallosses} \\
    CH$_2$ & 14.0157 \\
    CH$_4$ & 16.0313 \\
    NH$_3$ &  17.0265 \\
    H$_2$O & 18.0106 \\
    K$^+$ to NH$_4$$^+$" & 20.9293 \\
    Na$^+$ to H$^+$ & 21.9819 \\
    C$_2$H$_2$ & 26.0157 \\
    CO & 27.9949 \\
    C$_2$H$_4$ & 28.0313 \\
    CH$_3$N & 29.0266 \\
    CH$_2$O & 30.0106 \\
    CH$_5$N & 31.0422 \\
    S & 31.9721 \\
    H$_2$S & 33.9877 \\
    K$^+$to H$^+$ &  37.9559 \\
    C$_2$H$_2$O & 42.0106 \\
    C$_3$H$_6$ & 42.0470 \\
    CHNO & 43.0058 \\
    CO$_2$ & 43.9898 \\
    CH$_2$ O$_2$ & 46.0055 \\
    C$_4$H$_8$ & 56.0626 \\
    C$_3$H$_9$N & 59.0735 \\
    C$_2$H$_4$ O$_2$ & 60.0211 \\
    CH$_4$N$_2$O & 60.0324 \\
    SO$_2$ & 63.9619 \\
    C$_5$H$_8$ & 68.0626 \\
    C$_3$H$_6$ O$_2$ & 74.0368 \\
    C$_6$H$_6$ & 78.0470 \\
    SO$_3$ & 79.9568 \\
    C$_3$H$_2$O$_3$ & 86.0004 \\
    C$_4$H$_8$O$_2$ & 88.0517 \\
    C$_4$H$_{12}$N$_2$ & 88.1000 \\
    H$_2$(SO)$_4$ & 97.9674 \\
    H$_3$(PO)$_4$ & 97.9769 \\
    C$_5$H$_{10}$O$_2$ & 102.0618 \\
    C$_3$H$_4$O$_4$ & 104.0110 \\
    C$_6$H$_{12}$O$_2$ & 116.0861 \\
    C$_2$H$_5$O$_4$P & 123.9926 \\
    C$_5$H$_8$O$_4$ & 132.0423 \\
    C$_7$H$_{19}$N$_3$ & 145.1579 \\
    C$_6$H$_{10}$O$_4$ & 146.0579 \\
    C$_6$H$_{10}$O$_5$ & 162.0528 \\
    C$_6$H$_{12}$O$_5$ & 164.0685 \\ 
    C$_6$H$_8$O$_6$ & 176.0321 \\
    C$_6$H$_{12}$O$_6$ & 180.0634 \\
    C$_6$H$_{10}$O$_7$ & 194.0427 \\
    C$_8$H$_{12}$O$_6$ & 204.0655 \\
    C$_{11}$H$_{10}$O$_4$ & 206.0579 \\
    C$_{10}$H$_{15}$N$_3$ O$_6$ S & 305.0682 \\
    C$_{10}$H$_{17}$N$_3$ O$_6$ S & 307.0838 \\
    C$_{12}$H$_{20}$O$_{10}$ & 324.1057 \\
    C$_{12}$H$_{22}$O$_{11}$ & 342.1162 \\
    \hline
\end{longtable}


## Bibliography


